Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-04-14 doc/manuscript/ESSDmanuscript.Rmd
knit in new figures

@@

```{r fig_map, out.width = "15cm", echo = FALSE, fig.cap = "\\textbf{Map of sites in ForC shaded by number of records relavent to (circles) and transferred to (triangles) EFDB.} PLACEHOLDER. We need to add records transferred to EFDB. We also need to limit map to variables relavent to EFDB. It would also be good to add an underlying map of FAP ecozones"}
#this is for a two-column figure. for one-column figure, use {r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("figures_tables/PLACEHOLDER_World_Map_of_sites.png")
```

```{r fig_dominant_veg, out.width = "15cm", echo = FALSE, fig.cap = "\\textbf{Historgram of number of records in ForC relavent to (grey) and transferred to (black) EFDB.} PLACEHOLDER. We need to add axis labels and the two classes of records. "}
#this is for a two-column figure. for one-column figure, use {r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("figures_tables/PLACEHOLDER_Williams_Histogram_of_dominant_vegetation.png")
```

>>>>

#READING IN FILES TO GET FIGURES/ TABLES/ STATS 
path_to_dir <- dirname(dirname(getwd())) # get path to repo

# MOVE FIGURE FILES 
#traditional comparison
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub//Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/IPCC-EFDB-integration/doc/manuscript/figures_tables", "World_Map_of_sites_with_FAO_and_IPCC_data_sent.png", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/figures/", "World_Map_of_sites_with_FAO_and_IPCC_data_sent.png", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/IPCC-EFDB-integration/doc/manuscript/figures_tables")

@@

```{r fig_map, out.width = "15cm", echo = FALSE, fig.cap = "\\textbf{Map of sites in ForC shaded by number of records relavent to (circles) and transferred to (triangles) EFDB.} PLACEHOLDER. We need to add records transferred to EFDB. We also need to limit map to variables relavent to EFDB. It would also be good to add an underlying map of FAP ecozones"}
#this is for a two-column figure. for one-column figure, use {r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("figures_tables/World_Map_of_sites_with_FAO_and_IPCC_data_sent.png")
```

```{r fig_dominant_veg, out.width = "15cm", echo = FALSE, fig.cap = "\\textbf{Historgram of number of records in ForC relavent to (grey) and transferred to (black) EFDB.} PLACEHOLDER. We need to add axis labels and the two classes of records. "}
#this is for a two-column figure. for one-column figure, use {r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("figures_tables/Histogram_n_Relevant_and_Transferred_Records.png")
```

### 2022-04-14 doc/manuscript/ESSDmanuscript.tex
knit in new figures

As of April 13, 2022, ForC (v4.0) contained NA independent records (NA
total), NA of which were for variables relevant to EFDB (Fig. 1). These
records were distributed across all forested continents and ecozones,
with particularly high concentrations in \emph{{[}ecozone(s){]}} and low
concentrations in \emph{{[}ecozone(s){]}} (Fig. 2). The most widely
represented forest type was \emph{{[}type{]}}, followed by
\emph{{[}type{]}} and \emph{{[}type{]}} (Fig. 3).

\begin{figure}
\includegraphics[width=15cm]{figures_tables/PLACEHOLDER_World_Map_of_sites} \caption{\textbf{Map of sites in ForC shaded by number of records relavent to (circles) and transferred to (triangles) EFDB.} PLACEHOLDER. We need to add records transferred to EFDB. We also need to limit map to variables relavent to EFDB. It would also be good to add an underlying map of FAP ecozones}\label{fig:fig_map}
\end{figure}

\begin{figure}
\includegraphics[width=15cm]{figures_tables/PLACEHOLDER_Williams_Histogram_of_dominant_vegetation} \caption{\textbf{Historgram of number of records in ForC relavent to (grey) and transferred to (black) EFDB.} PLACEHOLDER. We need to add axis labels and the two classes of records. }\label{fig:fig_dominant_veg}
\end{figure}

@@

As of April 13, 2022, we had reviewed and sent NA, NA of which have been
reviewed, accepted, and posted (Fig. 2-3, Table 2). \emph{{[}DETAILS{]}}

>>>>

As of April 14, 2022, ForC (v4.0) contained NA independent records (NA
total), NA of which were for variables relevant to EFDB (Fig. 1). These
records were distributed across all forested continents and ecozones,
with particularly high concentrations in \emph{{[}ecozone(s){]}} and low
concentrations in \emph{{[}ecozone(s){]}} (Fig. 2). The most widely
represented forest type was \emph{{[}type{]}}, followed by
\emph{{[}type{]}} and \emph{{[}type{]}} (Fig. 3).

\begin{figure}
\includegraphics[width=15cm]{figures_tables/World_Map_of_sites_with_FAO_and_IPCC_data_sent} \caption{\textbf{Map of sites in ForC shaded by number of records relavent to (circles) and transferred to (triangles) EFDB.} PLACEHOLDER. We need to add records transferred to EFDB. We also need to limit map to variables relavent to EFDB. It would also be good to add an underlying map of FAP ecozones}\label{fig:fig_map}
\end{figure}

\begin{figure}
\includegraphics[width=15cm]{figures_tables/Histogram_n_Relevant_and_Transferred_Records} \caption{\textbf{Historgram of number of records in ForC relavent to (grey) and transferred to (black) EFDB.} PLACEHOLDER. We need to add axis labels and the two classes of records. }\label{fig:fig_dominant_veg}
\end{figure}

@@

As of April 14, 2022, we had reviewed and sent NA, NA of which have been
reviewed, accepted, and posted (Fig. 2-3, Table 2). \emph{{[}DETAILS{]}}
